Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
update capitalization of institutions in acknowledgments

The authors would like to thank PSL for funding this research, the CNSMDP for fruitfull collaboration and the IRCAM for providing access to the SOL database.

>>>>

The authors would like to thank PSL for funding this research, CNSMDP for fruitful collaboration and Ircam for providing access to the SOL database.
